# ILC water points


```{r}
pacman::p_load(
  tidyverse,
  sf,
  janitor
)
```

```{r}
ilc_villages <-
  wp_census %>%
  dplyr::filter(
    country == "Malawi",
    sample_group == "ILC"
  )
```

### Clusters

```{r}
ilc_villages %>%
  pull(ea_ilc_wpt) %>%
  n_distinct
```

```{r}
ilc_villages %>%
  dplyr::filter(
    (!is.na(wp_func) & ilc_wp) |
      (wp_func & ilc_wcp)
## Chlorination

```{r}
table <-
  list(
    "All water collection points" = ilc_villages %>% dplyr::filter(ilc_wcp),
    "Closest water collection point" = ilc_villages %>% dplyr::filter(ilc_wcp, closer),
    "Other water collection point" = ilc_villages %>% dplyr::filter(ilc_wcp, !closer)
  ) %>%
    map(
      ~ summarise(
        .,
        across(
          c(disctcr_02, discfcr_02, metertcr_02, meterfcr_02, metertcr_01, meterfcr_01),
          list(
            n = ~ sum(!is.na(.)),
            pct = ~ round((mean(., na.rm = TRUE) * 100), 1)
          )
        )
      )
    ) %>%
    bind_rows(.id = "group") %>%
  select(
    -c(discfcr_02_n, meterfcr_02_n, metertcr_01_n, meterfcr_01_n)
  ) %>%
  set_names(
    c("Water points", "N", "TCR ≥ 0.2 ppm", "FCR ≥ 0.2 ppm", "N", "TCR ≥ 0.2 ppm", "TCR ≥ 0.1 ppm", "FCR ≥ 0.2 ppm", "FCR ≥ 0.1 ppm")
  )
    
kable(
  table, 
  format = "html"
) %>%
  kable_styling(latex_options = c("scale_down", "HOLD_position")) %>%
  kable_paper("striped", full_width = TRUE) %>%
  add_header_above(c(" ", paste0("(", 1:8,")")), line = FALSE) %>%
  add_header_above(
    c(
      " ", 
      "Color wheel" = 3, 
      "Colorimeter" = 5
    )
  )
```

```{r}
kable(
  dosing, 
  format = "latex",
  escape = F,
  align = "c", 
  booktabs = T,
  caption = "Chlorine detection rates at water collection points connected to ILC",
  label = "ilc-cl"
) %>%
  kable_styling(latex_options = c("HOLD_position")) %>%
  add_header_above(c(" ", paste0("(", 1:8,")")), line = FALSE) %>%
  add_header_above(
    c(
      " ", 
      "Color wheel" = 3, 
      "Colorimeter" = 5
    )
  ) %>%
  writeLines(
    "output/tables/ilc-cl.tex"
  )
```

```{r}
functionality <-
  ilc_villages %>%
  summarise(
    ilc_wp = sum(ilc_wp & wp_func, na.rm = TRUE),
    ilc_wcp = sum(ilc_wcp & wp_func, na.rm = TRUE)
  )

func_clusters <-
  ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  summarise(
    clusters = 
  )
```
```{r}
ilc_villages %>%
  dplyr::filter(wp_func) %>%
  pull(ea_ilc_wpt) %>%
  n_distinct
```

```{r}
ilc_villages %>%
  dplyr::filter(
    !is.na(ilc_devicefunc)
  ) %>%
  pull(ea_ilc_wpt) %>%
  n_distinct
```

```{r}
ilc_villages %>%
  dplyr::filter(
    ilc_devicefunc
  ) %>%
  pull(ea_ilc_wpt) %>%
  n_distinct
```

### Water points

```{r}
ilc_villages %>%
  dplyr::filter(ilc_wp) %>%
  tabyl(wp_func) %>%
  adorn_totals()
```

```{r}
ilc_villages %>%
  dplyr::filter(ilc_wp) %>%
  tabyl(ilc_devicefunc) %>%
  adorn_totals()
```

### Water collection points

```{r}
ilc_villages %>%
  dplyr::filter(ilc_wcp) %>%
  tabyl(wp_func) %>%
  adorn_totals()
```

```{r}
ilc_villages %>%
  dplyr::filter(ilc_wcp) %>%
  tabyl(wp_func) %>%
  adorn_totals()
```

```{r}
ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  dplyr::filter(any(ilc_wp & wp_func)) %>%
  ungroup %>%
  summarise(
    wcp = sum(ilc_wcp),
    func = sum(ilc_wcp & wp_func)
  )
```


```{r}
ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  dplyr::filter(any(wp_func)) %>%
  ungroup %>%
  summarise(
    wcp = sum(ilc_wcp),
    func = sum(ilc_wcp & wp_func)
  )
```

```{r}
ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  dplyr::filter(any(!is.na(ilc_devicefunc))) %>%
  ungroup %>%
  summarise(
    wcp = sum(ilc_wcp)
  )
```

```{r}
ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  dplyr::filter(any(wp_func)) %>%
  ungroup %>%
  summarise(
    wcp = sum(ilc_wcp),
    func = sum(ilc_wcp & wp_func)
  )
```

```{r}
ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  dplyr::filter(any(ilc_devicefunc)) %>%
  ungroup %>%
  summarise(
    wcp = sum(ilc_wcp)
  )
```

#scrap

```{r}
evac_dsw <-
  villages %>%
  dplyr::filter(village_id %in% ilc_villages$village_id, dsw) %>%
  summarise(
    group = "DSW",
    evac_villages = n_distinct(village_id),
    evac_wps = sum(dsw_wpt)
  )

evac_wpt <-
  villages %>%
  dplyr::filter(village_id %in% ilc_villages$village_id, ilc_wpt_yn == 1) %>%
  summarise(
    group = "ILC Water Point",
    evac_villages = n_distinct(village_id),
    evac_wps = sum(ilc_wpt)
  )

evac_wcp <-
  villages %>%
  dplyr::filter(village_id %in% ilc_villages$village_id, ilc_wcp_yn == 1) %>%
  summarise(
    group = "ILC Water Collection Point",
    evac_villages = n_distinct(village_id),
    evac_wps = sum(ilc_wcp)
  )
  
dsw <-
  wp_census %>% 
  dplyr::filter(dsw, sample_group == "ILC") %>%
  summarise(
    group = "DSW",
    wpc_villages = n_distinct(village_id),
    wpc_wps = n(),
    communal = sum(wp_multicompound),
    matched = sum(!is.na(ea_id)),
    func = sum(wp_func),
    func_pct = func/wpc_wps
  ) %>%
  transmute(
    group,
    wpc_villages, wpc_wps, clusters = "",
    communal, matched, 
    func = paste0(" ", func, " (", round(func_pct * 100, 1), "%)"),
    wpt_checked = "",
    device_func = "",
  )

ilc_wpt <-
  wp_census %>% 
  dplyr::filter(ilc_wp, sample_group == "ILC") %>%
  summarise(
    group = "ILC Water Point",
    wpc_villages = n_distinct(village_id),
    wpc_wps = n(),
    communal = sum(wp_multicompound),
    matched = sum(!is.na(ea_id)),
    clusters = n_distinct(ilc_cluster_id),
    func = sum(wp_func),
    func_pct = func/wpc_wps,
    wpt_checked = sum(!is.na(ilc_devicefunc)),
    device_func = sum(ilc_devicefunc, na.rm = TRUE),
    device_func_pct = device_func/func
  ) %>%
  transmute(
    group,
    wpc_villages, wpc_wps,
    communal, matched, 
    clusters = as.character(clusters),
    func = paste0(" ", func, " (", round(func_pct * 100, 1), "%)"),
    wpt_checked = wpt_checked %>% as.character,
    device_func = paste0(device_func, " (", round(device_func_pct * 100, 1), "%)"),
  )

ilc_wcp <-
  ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  mutate(ilc_devicefunc = max(ilc_devicefunc)) %>%
  dplyr::filter(ilc_wcp, sample_group == "ILC") %>%
  ungroup %>%
  summarise(
    group = "ILC Water Collection Point",
    wpc_villages = n_distinct(village_id),
    wpc_wps = n(),
    communal = sum(wp_multicompound),
    matched = sum(!is.na(ea_id)),
    clusters = n_distinct(ilc_cluster_id),
    func = sum(wp_func),
    func_pct = func/wpc_wps,
    wpt_checked = sum(!is.na(ilc_devicefunc)),
    device_func = sum(ilc_devicefunc, na.rm = TRUE),
    device_func_pct = device_func/wpt_checked
  ) %>%
  transmute(
    group,
    wpc_villages, wpc_wps,
    communal, matched, 
    clusters = as.character(clusters),
    func = paste0(func, " (", round(func_pct * 100, 1), "%)"),
    wpt_checked = as.character(wpt_checked),
    device_func = paste0(device_func, " (", round(device_func_pct * 100, 1), "%)"),
  )

ilc_func <-
  evac_dsw %>%
  bind_rows(evac_wpt) %>%
  bind_rows(evac_wcp) %>%
  left_join(
    dsw %>%
    bind_rows(ilc_wpt) %>%
    bind_rows(ilc_wcp)
  )

ilc_func %>%
  kable(
    format = "html"
  ) %>%
  kable_paper("striped", full_width = TRUE)
  # add_header_above(
  #   c(
  #     " " = 2,
  #     "Number of WPs" = 2,
  #     "Percent of water points in the census" = 6
  #   ),
  #   line = TRUE
  # ) %>%
  # add_header_above(
  #   c(" ", paste0("(", 1:9,")")), 
  #   line = FALSE
  # )
```

there are missing values on closer for WCPs!

```{r}
ilc_wpt <-
  wp_census %>% 
  dplyr::filter(ilc_wp, sample_group == "ILC") %>%
  summarise(
    group = "ILC Water Point",
    villages = n_distinct(village_id),
    wpc_wps = n(),
    func = sum(wp_func),
    func_pct = func/wpc_wps,
    device_func = sum(ilc_devicefunc, na.rm = TRUE),
    device_func_pct = device_func/func
  )

ilc_wcp <-
  ilc_villages %>%
  group_by(ea_ilc_wpt) %>%
  mutate(ilc_devicefunc = max(ilc_devicefunc)) %>%
  dplyr::filter(ilc_wcp, sample_group == "ILC") %>%
  ungroup %>%
  summarise(
    group = "ILC Water Collection Point",
    villages = n_distinct(village_id),
    wpc_wps = n(),
    func = sum(wp_func),
    func_pct = func/wpc_wps,
    wpt_checked = sum(!is.na(ilc_devicefunc)),
    device_func = sum(ilc_devicefunc, na.rm = TRUE),
    device_func_pct = device_func/wpt_checked,
    tested = sum(wp_func & !is.na(disctcr_02)),
    closer = sum(wp_func & closer & !is.na(disctcr_02)),
    closer_tcr = sum(wp_func & closer & !is.na(disctcr_02) & disctcr_02),
    not_closer = sum(!closer & !is.na(disctcr_02), na.rm = TRUE),
    not_closer_pct = mean(not_closer & disctcr_02, na.rm = TRUE)/not_closer
  )

ilc_dosing <-
  ilc_wpt %>%
  bind_rows(ilc_wcp) %>%
  mutate(
    across(
      ends_with("pct"),
      ~ round(. * 100, 1) %>% paste0("%")
    )
  )

ilc_dosing %>%
  kable(
    format = "html"
  ) %>%
  kable_paper("striped", full_width = TRUE)
  # add_header_above(
  #   c(
  #     " " = 2,
  #     "Number of WPs" = 2,
  #     "Percent of water points in the census" = 6
  #   ),
  #   line = TRUE
  # ) %>%
  # add_header_above(
  #   c(" ", paste0("(", 1:9,")")), 
  #   line = FALSE
  # )
```

# Scrap


## Villages

```{r}
wp_census %>%
  dplyr::filter(sample_group == "ILC") %>%
  group_by(country) %>%
  summarise(
    villages = n_distinct(village_id),
    ilc_villages = case_when(
      ilc ~ village_id
    ) %>% na.omit %>% n_distinct,
    wps = n_distinct(wp_id),
    ilc = sum(ilc),
    dsw = sum(dsw)
  )
```


```{r}
wps_ilc_villages <-
  wp_census %>%
  dplyr::filter(sample_group == "ILC", country == "Malawi") %>%
  group_by(village_id) %>%
  dplyr::filter(
    any(ilc_wp) | any(ilc_wcp)
  ) %>%
  mutate(
    analysis = wp_multicompound & wp_drink & wp_func,
    ilc_wp_func = ilc_wp & wp_func,
    ilc_wcp_func = ilc_wcp & wp_func,
    dsw_func = dsw & wp_func,
  )
```

```{r}
wps_ilc_villages %>% tabyl(ilc_wp, ilc_wcp)
```


```{r}
wps_ilc_villages %>% 
  group_by(village_id, country) %>%
  summarise(
    villages = n(),
    across(
      c(dsw, dsw_func, ilc_wp, ilc_wp_func, ilc_wcp, ilc_wcp_func),
      ~ any(.)
    )
  ) %>%
  group_by(country) %>%
  summarise(
    count = n(),
    across(
      c(dsw, dsw_func, ilc_wp, ilc_wp_func, ilc_wcp, ilc_wcp_func),
      ~ sum(.)
    )
  )
```

## Clusters

```{r}
ilc_villages %>% 
  pull(ea_ilc_wpt) %>%
  n_distinct
```

```{r}
ilc_villages %>%
  dplyr::filter(str_detect(intervention_type, "ILC")) %>%
  group_by(ea_ilc_wpt, country) %>%
  summarise(
    wp_func = max(wp_func * 1),
    wp_multicompound = max(wp_multicompound * 1),
    tested = max(!is.na(disctcr) * 1)
  ) %>%
  summarise(
    n = n(),
    across(
      c(wp_func, wp_multicompound, tested),
      ~ sum(.)
    )
  )
```


## Communal water points

```{r}
ilc_villages %>%
  dplyr::filter(ilc) %>%
  group_by(ilc_wp) %>%
  summarise(
    n = n(),
    sum(wp_multicompound),
    sum(ilc_wcp)
  )
```


## Functionality 

```{r}
ilc_villages %>%
  group_by(country) %>%
  summarise(
    wps = n(),
    across(
      c(dsw, dsw_func, ilc_wp, ilc_wp_func, ilc_wcp, ilc_wcp_func),
      ~ sum(.)
    )
  )
```

```{r}

```


```{r}
ilc_villages %>% mutate(tested = !is.na(disctcr)) %>%
  
  group_by(intervention_type) %>%
  summarise(
    count = n(),
    across(
      c(wp_multicompound, wp_drink, wp_func, analysis, tested),
      ~ sum(., na.rm = TRUE)
    )
  )
```
```{r}
ilc_villages %>% 
  dplyr::filter(ilc_wcp) %>%
  summarise(
    count = n(),
    across(
      c(wp_multicompound, wp_drink, wp_func, analysis),
      ~ sum(., na.rm = TRUE)
    )
  )
```

## Expected sample

```{r}
villages <-
  read_rds(
    file.path(
      path_box,
      "Data",
      "Villages",
      "DataSets",
      "Final",
      "villages.rds"
    )
  )
```

```{r}
villages %>%
  dplyr::filter(village_id %in% ilc_villages$village_id) %>%
  summarise(
    n = n(),
    across(
      c(dsw_wpt, ilc_wpt, ilc_wcp),
      ~ sum(.)
    )
  )
```

## Number of WPs and WCPs

```{r}
ilc_villages %>%
  dplyr::filter(!is.na(ea_id)) %>% tabyl(ilc_wp, ilc_wcp) %>%
  group_by(ea_ilc_wpt) %>%
  summarise(n = n()) %>%
  tabyl(n) %>%
  adorn_totals()
```



## Water testing

```{r}
ilc_villages %>%
  dplyr::filter(ilc, closer) %>%
  mutate(id = coalesce(ea_id, wp_id)) %>%
  summarise()
```



### Water testing

```{r}
closer <-
  ilc_villages %>%
  dplyr::filter(ilc, closer) %>%
  ungroup %>%
  summarise(
    across(
      c(meterfcr_01, metertcr_01, meterfcr_02, metertcr_02, discfcr_02, disctcr_02),
      list(
        tests = ~ sum(!is.na(.)),
        mean = ~ mean(., na.rm = TRUE)
      )
    )
  ) %>%
  mutate(
    sample = "closest"
  )

all <-
  ilc_villages %>%
  dplyr::filter(ilc) %>%
  ungroup %>%
  summarise(
    across(
      c(meterfcr_01, metertcr_01, meterfcr_02, metertcr_02, discfcr_02, disctcr_02),
      list(
        tests = ~ sum(!is.na(.)),
        mean = ~ mean(., na.rm = TRUE)
      )
    )
  ) %>%
  mutate(
    sample = "all"
  )
```

```{r}
closer %>%
  bind_rows(all) %>%
  pivot_longer(
    cols = -c(sample),
    names_pattern = "(.*)_(..)_(.*)",
    names_to = c("test", "threshold", ".value")
  ) %>%
  mutate(
    mean = round(mean * 100, 1),
    res = str_sub(test, -3, -1) %>% str_to_upper,
    test = str_sub(test, 1, -4)
  ) %>%
  pivot_wider(
    id_cols = c(test, threshold, res),
    values_from = c(tests, mean),
    names_from = c(sample)
  ) %>%
  arrange(test, desc(threshold), desc(res)) %>%
  select(
    res,
    contains("closest"),
    contains("all")
  ) %>%
  kable(
    col.names = c(
      " ",
      "N", "Detected (%)",
      "N", "Detected (%)"
    ),
    format = "html",
    align = "c"
  ) %>%
  add_header_above(
      c(" " = 1, "Nearest water collection points" = 2, "All water collection points" = 2)
  ) %>%
  group_rows("Color disc reading > 0.2ppm", 1, 2) %>%
  group_rows("Colorimeter reading > 0.2ppm", 3, 4) %>%
  group_rows("Colorimeter reading > 0.1ppm", 5, 6) %>%
  kable_paper("striped", full_width = F)
```

```{r}
ilc_villages %>%
  dplyr::filter(ilc, wp_func, ilc_) %>%
  mutate(closer = replace_na(closer, FALSE)) %>%
  group_by(closer) %>%
  summarise(
    across(
      c(meterfcr_01, metertcr_01, meterfcr_02, metertcr_02, discfcr_02, disctcr_02),
      list(
        tests = ~ sum(!is.na(.)),
        mean = ~ mean(., na.rm = TRUE)
      )
    )
  )
```


```{r}
ilc_villages %>%
  dplyr::filter(ilc_wp) %>%
  group_by(ea_id) %>%
  summarise(
    across(
      c(meterfcr_01, metertcr_01, meterfcr_02, metertcr_02, discfcr_02, disctcr_02),
      list(
        tests = ~ sum(!is.na(.)),
        mean = ~ sum(., na.rm = TRUE),
        ntested = ~ any(!is.na(.)),
        anytested = ~ if_else(any(!is.na(.)), any(., na.rm = TRUE), NA),
        alltested = ~ if_else(any(!is.na(.)), all(., na.rm = TRUE), NA),
        any = ~ if_else(any(!is.na(.)), any(., na.rm = TRUE), FALSE),
        all = ~ if_else(any(!is.na(.)), all(., na.rm = TRUE), FALSE)
      )
    )
  ) %>%
  pivot_longer(
    cols = -ea_id,
    names_pattern = "(.*)_(.*)_(.*)",
    names_to = c("measure", "threshold", ".value")
  ) %>%
  group_by(measure, threshold) %>%
  summarise(
    tests = sum(tests),
    mean = sum(mean)/tests,
    ntested = sum(ntested),
    anytested = mean(anytested, na.rm = TRUE),
    alltested = mean(alltested, na.rm = TRUE),
    n = n(),
    any = mean(any, na.rm = TRUE),
    all = mean(all, na.rm = TRUE)
  ) %>%
  ungroup %>%
  arrange(desc(threshold), measure) %>%
  mutate(
    across(
      c(mean, contains("any"), contains("all")),
      ~ round(. * 100, 1)
    ),
    label = c(
      "Color wheel FCR >= 0.2 mg/L",
      "Color wheel TCR >= 0.2 mg/L",
      "Meter FCR >= 0.2 mg/L",
      "Meter TCR >= 0.2 mg/L",
      "Meter FCR >= 0.1 mg/L",
      "Meter TCR >= 0.1 mg/L"
    )
  ) %>%
  select(-c(threshold, measure)) %>%
  select(label, everything()) %>%
  kable(
    col.names = c(
      "Detection criterion",
      "N", "Detected (%)",
      "N", "Detected at closest water collection point (%)", "Detected at all water collection points (%)",
      "N", "Detected at closest water collection point (%)", "Detected at all water collection points (%)"
    ),
    format = "html",
    align = "c"
  ) %>%
  #add_row(c("", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)", "(7)", "(8)")) %>%
  add_header_above(c(" " = 1, "Tests" = 2, "Working ILC devices" = 3, "All ILC devices" = 3)) %>%
  kable_paper("striped", full_width = F) %>%
  footnote(general = "Columns 4 to 8 group tests based on the ILC device they are connected. Detection rates in columns 5 and 6 use the number of water points with ILC that were functional (and therefore tested) as the denominator. Detection rates in columns 7 and 8 use the number of water points with ILC that serve water collection points in the census (including those that were not functioning at the time of the visit) as the denominator.")
  
```

### All water collection points

```{r}
all <-
  ilc_villages %>%
  dplyr::filter(ilc_wcp) %>%
  group_by(ea_id) %>%
  summarise(
    across(
      c(meterfcr_01, metertcr_01, meterfcr_02, metertcr_02, discfcr_02, disctcr_02),
      list(
        n = ~ any(!is.na(.)),
        all = ~ if_else(any(!is.na(.)), all(., na.rm = TRUE), NA)
      )
    )
  ) %>%
  pivot_longer(
    cols = -ea_id,
    names_pattern = "(.*)_(.*)_(.*)",
    names_to = c("measure", "threshold", ".value")
  ) %>%
  group_by(measure, threshold) %>%
  summarise(
    n = sum(n),
    all_tested = mean(all, na.rm = TRUE)
  )
```


Individual water points

```{r}
ind <-
  ilc_villages %>%
  dplyr::filter(str_detect(intervention_type, "ILC")) %>%
  summarise(
    across(
      c(meterfcr_01, metertcr_01, meterfcr_02, metertcr_02, discfcr_02, disctcr_02),
      list(
        n = ~ sum(!is.na(.)),
        mean = ~ mean(., na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    cols = everything(),
    names_pattern = "(.*)_(.*)_(.*)",
    names_to = c("measure", "threshold", ".value")
  ) %>%
  arrange(desc(threshold), measure) %>%
  mutate(mean = round(mean * 100, 1))
```

Tested clusters

```{r}
ilc_villages %>%
  dplyr::filter(str_detect(intervention_type, "ILC"), !is.na(disctcr)) %>%
  group_by(ea_ilc_wpt) %>%
  summarise(
    across(
      c(meterfcr, metertcr, discfcr, disctcr),
      ~ mean(., na.rm = TRUE)
    ),
    across(
      c(
        meterfcr_01, metertcr_01, 
        meterfcr_02, metertcr_02, 
        discfcr_02, disctcr_02
      ),
      ~ any(., na.rm = TRUE)
    )
  ) %>%
  mutate(
    across(
      c(meterfcr, metertcr, discfcr, disctcr),
      list(
        `mean01` = ~ . > 0.1,
        `mean02` = ~ . > 0.2
      )
    )
  ) %>%
  select(
    -c(meterfcr, metertcr, discfcr, disctcr, ea_ilc_wpt)
  ) %>%
  summarise(
    across(
      everything(),
      list(
        n = ~ sum(!is.na(.)),
        mean = ~ mean(., na.rm = TRUE)
      ),
      .names = "{.col}.{.fn}"
    )
  ) %>%
  pivot_longer(
    cols = everything(),
    names_pattern = "(.*)[.](.*)",
    names_to = c("measure", ".value")
  ) %>%
  mutate(
    type = str_detect(measure, "mean"),
    measure = measure %>%
      str_remove_all("mean")
  ) %>%
  pivot_wider(
    values_from = c(n, mean),
    names_from = type
  ) %>%
  mutate(
    threshold = str_sub(measure, -2),
    across(
      contains("mean"),
      ~ round(. * 100, 1)
    )
  ) %>%
  dplyr::filter(!is.na(n_FALSE)) %>%
  select(measure,n_FALSE, mean_FALSE, everything()) %>%
  arrange(desc(threshold), measure)
```


All clusters

```{r}
ilc_villages %>%
  dplyr::filter(str_detect(intervention_type, "ILC")) %>%
  group_by(ea_ilc_wpt) %>%
  summarise(
    across(
      c(meterfcr, metertcr, discfcr, disctcr),
      ~ mean(., na.rm = TRUE)
    ),
    across(
      c(
        meterfcr_01, metertcr_01, 
        meterfcr_02, metertcr_02, 
        discfcr_02, disctcr_02
      ),
      ~ any(., na.rm = TRUE)
    )
  ) %>%
  mutate(
    across(
      c(meterfcr, metertcr, discfcr, disctcr),
      list(
        `mean01` = ~ . > 0.1,
        `mean02` = ~ . > 0.2
      )
    )
  ) %>%
  select(
    -c(meterfcr, metertcr, discfcr, disctcr, ea_ilc_wpt)
  ) %>%
  summarise(
    n = n(),
    across(
      everything(),
      list(
        mean = ~ sum(., na.rm = TRUE)/n
      ),
      .names = "{.col}.{.fn}"
    )
  ) %>%
  pivot_longer(
    cols = contains("mean"),
    names_pattern = "(.*)[.](.*)",
    names_to = c("measure", ".value")
  ) %>%
  mutate(
    type = str_detect(measure, "mean"),
    measure = measure %>%
      str_remove_all("mean")
  ) %>%
  pivot_wider(
    values_from = mean,
    names_from = type
  ) %>%
  mutate(
    threshold = str_sub(measure, -2),
    across(
      c(`FALSE`, `TRUE`),
      ~ round(. * 100, 1)
    )
  ) %>%
  dplyr::filter(!is.na(`FALSE`), !is.na(`TRUE`)) %>%
  arrange(desc(threshold), measure)
```

## donté now



```{r}
ilc_villages %>%
  dplyr::filter(ilc_wp) %>%
  select(wp_id, village_id, wp_drink, wp_multicompound, wp_func, meterfcr_01, metertcr_01, discfcr_02, disctcr_02, contains("comments")) %>%
  view
```

```{r}
ilc_villages %>%
  dplyr::filter(ilc_wp, analysis) %>%
  select(wp_id, village) %>%
  left_join(constructed, by = c("wp_id" = "wp_id_c")) %>%
  select(wp_id, ea_id, ea_ilc_wpt, village_id, wp_drink, wp_multicompound, wp_func, wp_ilc_device_c, wp_ilc_evac ,contains("comments")) %>%
  view
```

```{r}
ilc_villages %>%
  dplyr::filter(!is.na(meterfcr) | !is.na(metertcr) | !is.na(discfcr) | !is.na(disctcr)) %>% 
  select(wp_id, village) %>%
  left_join(constructed, by = c("wp_id" = "wp_id_c")) %>%
  summarise(
    count = n(),
    wps = n_distinct(ea_ilc_wpt)
  )
```
```{r}
ilc_villages %>%
  dplyr::filter(!is.na(meterfcr) | !is.na(metertcr) | !is.na(discfcr) | !is.na(disctcr)) %>% 
  select(wp_id, village) %>%
  left_join(constructed, by = c("wp_id" = "wp_id_c")) %>%
  summarise(
    count = n(),
    wps = n_distinct(ea_ilc_wpt)
  )
```

```{r}
ilc_villages %>%
  dplyr::filter(!is.na(meterfcr) | !is.na(metertcr) | !is.na(discfcr) | !is.na(disctcr), intervention_type != "DSW") %>% 
  select(wp_id, village) %>%
  left_join(constructed, by = c("wp_id" = "wp_id_c")) %>%
  select(wp_id, ea_id, ea_ilc_wpt, village_id, meterfcr, metertcr, discfcr, disctcr, contains("comments")) %>%
  write_csv(
    "C:/Users/luizaandrade/Downloads/ilc.csv"
  )
```

```{r}
cluster_level <-
  ilc_villages %>%
  dplyr::filter(str_detect(intervention_type, "ILC")) %>% 
  group_by(ea_ilc_wpt) %>%
  mutate(
    across(
      c(wp_func, wp_drink, wp_multicompound),
      ~ as.numeric(.)
    )
  ) %>%
  skim(meterfcr, metertcr, discfcr, disctcr, wp_func, wp_drink, wp_multicompound)

    found = n(),
    across(
      c(meterfcr, metertcr, discfcr, disctcr),
      list(
        tests = ~sum(!is.na(.)),
        min = ~ min(.),
        max = ~ max(.),
        mean = ~ mean(., na.rm = TRUE),
        var = ~ var(., na.rm = TRUE)
      )
    )
  )
```

```{r}
ilc_villages %>%
  dplyr::filter(intervention_type != "DSW") %>% 
  summarise(
    across(
      c()
    )
  ) select(wp_id, ea_id, ea_ilc_wpt, village_id, meterfcr, metertcr, discfcr, disctcr, contains("comments")) %>%
  write_csv(
    "C:/Users/luizaandrade/Downloads/ilc.csv"
  )
```


```{r}
ilc %>%
  dplyr::filter(
    country == "Malawi",
    str_detect(intervention_type, "ILC water point"),
    sample_group == "ILC",
  ) %>%
  select(wp_id, village_id, intervention_type, ea_id, ea_ilc_wpt, wp_func, everything()) %>%
  view
```




## Number of tests

```{r}
ilc %>%
  group_by(intervention_type) %>%
  summarise(
    found = n(),
    functional = sum(wp_func),
    across(
      c(disctcr, discfcr, metertcr, meterfcr),
      ~ sum(!is.na(.))
    )
  )
```


```{r}
ilc %>%
  dplyr::filter(intervention_type == "ILC water point", wp_func) %>%
  view
```



