---
output: rmdformats::robobook
---

# Household-level chlorine residual tests

```{r}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(stringr)
library(sf)
library(tidyverse)
library(modelsummary)
library(fixest)
library(janitor)
library(kableExtra)
library(vtable)


path_box <- file.path(Sys.getenv("BOX"), "i-h2o-takeup")
path_git <- file.path(Sys.getenv("GITHUB"), "i-h2o-takeup")
theme <-
  theme_minimal() +
  theme(
    strip.background = element_rect(
      fill = "gray90",
      color = "gray90"
    ),
    plot.title = element_text(hjust = 0.5),
    text = element_text(size = 11, family = "Times"),
    plot.caption = element_text(
      hjust = 0,
      size = 10,
      color = "gray40"
    ),
    legend.position = "bottom"
  )
```

```{r}
hh_final <-
  read_rds(
    file.path(
      path_box,
      "Data",
      "HouseholdSurvey",
      "DataSets",
      "Final",
      "hh-survey.rds"
    )
  ) 

hh_test <-
  read_rds(
    file.path(
      path_box,
      "Data",
      "HouseholdSurvey",
      "DataSets",
      "Constructed",
      "hh-survey-chlorine.rds"
    )
  ) 

hh_constructed <-
  read_rds(
    file.path(
      path_box,
      "Data",
      "HouseholdSurvey",
      "DataSets",
      "Constructed",
      "hh-survey-constructed.rds"
    )
  ) 

hh <-
  hh_final %>%
  dplyr::filter(!is.na(country)) %>%
  select(
    key, survey, sample_group,
    household_id, country, village_id, district_id, wp_id,
    wp_intervention, wp_intervention_type, wp_func, wp_sourcetype,
    ilc, dsw, ilc_wp, ilc_wcp, 
    wp_dsw_dose, wp_dsw_chlorine, 
    watertreat_any, watertreat_boil, watertreat_dispcl, watertreat_othercl,
    howlong_waterprep, where_collect, who_collected, 
    int_warned, int_promoter,
    storage, access_contain, cover_storage,
    hhh_age, hhh_sex, hhh_educ, age_child,
    hh_pregnant, hh_under5, hh_under2,
    wp_turbidity, wp_pay,
    hh_dsw, hh_ilc,
    contains("flag"), contains("photo"), contains("pic")
  ) %>%
  left_join(
    hh_test, .,
    relationship = "many-to-one"
  ) 

test_long <-
  hh %>%
  pivot_longer(
    cols = c(matches("(*.)cr_c$"), matches("(*.)cr_color$")),
    names_pattern = "(.*)(...)_(.*)",
    names_to = c("instrument", "test", ".value")
  ) %>%
  rename(
    value = c
  ) %>%
  mutate(
    instrument = case_when(
      instrument == "meter" ~ "Colorimeter",
      instrument == "disc" ~ "Color wheel"
    ),
    test = test %>% str_to_upper,
    sourcetype = 
      case_when(
        wp_sourcetype == "River, stream, or other flowing water source" ~ "Flowing water source",
        wp_sourcetype ==  "Lake, pond, dam, or other standing water source" ~ "Standing water source",
        TRUE ~ wp_sourcetype %>% 
          str_replace_all("not powered by solar/electricity", "(not powered)") %>%
          str_replace_all("powered by solar/electricity", "(powered)")
      )
  )
```

## Number of observations

```{r}
hh %>%
  group_by(country, survey) %>%
  summarise(
    across(
      c(household_id, wp_id, village_id),
      ~ n_distinct(.)
    ),
    across(
      c(disctcr_c, discfcr_c, metertcr_c, meterfcr_c),
      ~ sum(!is.na(.))
    )
  ) %>%
  ungroup %>%
  select(-country) %>%
  kable(
    format = "html",
    col.names = c(
      "Survey",
      "Households", "Water points", "Villages",
      "TCR", "FCR", "TCR", "FCR"
    )
  ) %>%
  pack_rows("Malawi", 1, 2) %>%
  pack_rows("Uganda", 3, 4) %>%
  pack_rows("Unmatched", 5, 5) %>%
  add_header_above(c(" " = 4, "Color wheel" = 2, "Colorimeter" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

## Number of flags

Flagged observations will be removed for sensitivity checks

```{r}
hh %>%
  transmute(
    country,
    flag_low_quality,
    flag_disccomp = discfcr_c > disctcr_c,
    flag_disctcrcolor = disctcr_c >= 0.2 & disctcr_color == "1 - Clear",
    flag_discfcrcolor = discfcr_c >= 0.2 & discfcr_color == "1 - Clear",
    flag_metercomp = meterfcr_c > metertcr_c,
    flag_metertcrcolor = metertcr_c >= 0.2 & metertcr_color == "1 - Clear",
    flag_meterfcrcolor = meterfcr_c >= 0.2 & meterfcr_color == "1 - Clear",
  ) %>%
  group_by(country) %>%
  summarise(
    N = n(),
    across(
      everything(),
      ~ sum(., na.rm = TRUE)
    )
  ) %>%
  kable(
    format = "html",
    col.names = c(
      "Country", "N",
      "Low quality reading",
      "FCR > TCR", "TCR >= 0.2 on clear water", "FCR >= 0.2 on clear water",
      "FCR > TCR", "TCR >= 0.2 on clear water", "FCR >= 0.2 on clear water"
    )
  ) %>%
  add_header_above(c(" " = 3, "Color wheel" = 3, "Colorimeter" = 3)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

## Descriptives

### Distribution of readings

The maximum value in the color disc is 3.5, and in the colorimeter it's 2.2. When readings exceed 2.2, the colorimeter threw an error. These observations are replaced with 2.4.

```{r}
test_long %>%
  ggplot(
    aes(
      y = after_stat(density),
      x = value,
      fill = country
    )
  ) +
  geom_histogram(
    position = "identity",
    alpha = .5
  ) +
  facet_grid(test ~ instrument) +
  theme
```

### TCR and FCR readings

```{r}
test_long %>%
  pivot_wider(
    names_from = test,
    values_from = value
  ) %>% 
  ggplot(
    aes(
      x = FCR,
      y = TCR,
      color = country
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.1,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dotted"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(
    position = "jitter",
    alpha = .5
  ) +
  theme +
  facet_wrap(~ instrument, scales = "free") +
  scale_color_viridis_d()
```

### Dosage and chlorine residual

```{r}
test_long %>%
  ggplot(
    aes(
      y = wp_dsw_dose,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

### Reported color and chlorine residual

```{r}
test_long %>%
  ggplot(
    aes(
      y = color,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

### Reported source type and chlorine residual

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(sourcetype)) %>%
  group_by(country, instrument, sourcetype, test) %>%
  summarise(value = sum(!is.na(value))) %>%
  dplyr::filter(test == "TCR") %>%
  pivot_wider(
    values_from = value,
    names_from = instrument
  ) %>%
  ungroup %>%
  arrange(desc(`Color wheel`)) %>%
  pivot_wider(
    values_from = c(`Color wheel`, Colorimeter),
    names_from = country
  ) %>%
  select(
    sourcetype, 
    ends_with("Malawi"),
    ends_with("Uganda")
  ) %>%
  kable(
    format = "html",
    col.names = c("Source type", "Color wheel", "Colorimeter", "Color wheel", "Colorimeter")
  ) %>%
  add_header_above(c(" " = 1, "Malawi" = 2, "Uganda" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(sourcetype)) %>%
  group_by(country, sourcetype, instrument, test) %>%
  dplyr::filter(n() > 50) %>%
  ungroup %>%
  ggplot(
    aes(
      y = sourcetype,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

### Turbity and chlorine residual

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(wp_turbidity)) %>%
  group_by(country, instrument, wp_turbidity, test) %>%
  summarise(value = sum(!is.na(value))) %>%
  dplyr::filter(test == "TCR") %>%
  pivot_wider(
    values_from = value,
    names_from = instrument
  ) %>%
  ungroup %>%
  arrange(desc(`Color wheel`)) %>%
  pivot_wider(
    values_from = c(`Color wheel`, Colorimeter),
    names_from = country
  ) %>%
  select(
    wp_turbidity, 
    ends_with("Malawi"),
    ends_with("Uganda")
  ) %>%
  kable(
    format = "html",
    col.names = c("Turbidity", "Color wheel", "Colorimeter", "Color wheel", "Colorimeter")
  ) %>%
  add_header_above(c(" " = 1, "Malawi" = 2, "Uganda" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(wp_turbidity)) %>%
  group_by(country, wp_turbidity, instrument, test) %>%
  dplyr::filter(n() > 50) %>%
  ungroup %>%
  ggplot(
    aes(
      y = wp_turbidity,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

### Time since chlorination

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(howlong_waterprep)) %>%
  group_by(country, instrument, howlong_waterprep, test) %>%
  summarise(value = sum(!is.na(value))) %>%
  dplyr::filter(test == "TCR") %>%
  pivot_wider(
    values_from = value,
    names_from = instrument
  ) %>%
  ungroup %>%
  arrange(desc(`Color wheel`)) %>%
  pivot_wider(
    values_from = c(`Color wheel`, Colorimeter),
    names_from = country
  ) %>%
  select(
    howlong_waterprep, 
    ends_with("Malawi"),
    ends_with("Uganda")
  ) %>%
  kable(
    format = "html",
    col.names = c("Source type", "Color wheel", "Colorimeter", "Color wheel", "Colorimeter")
  ) %>%
  add_header_above(c(" " = 1, "Malawi" = 2, "Uganda" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(howlong_waterprep)) %>%
  group_by(country, howlong_waterprep, instrument, test) %>%
  dplyr::filter(sum(!is.na(value)) > 40) %>%
  ungroup %>%
  ggplot(
    aes(
      y = howlong_waterprep,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

### Source of tested water

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(where_collect)) %>%
  group_by(country, instrument, where_collect, test) %>%
  summarise(value = sum(!is.na(value))) %>%
  dplyr::filter(test == "TCR") %>%
  pivot_wider(
    values_from = value,
    names_from = instrument
  ) %>%
  ungroup %>%
  arrange(desc(`Color wheel`)) %>%
  pivot_wider(
    values_from = c(`Color wheel`, Colorimeter),
    names_from = country
  ) %>%
  select(
    where_collect, 
    ends_with("Malawi"),
    ends_with("Uganda")
  ) %>%
  kable(
    format = "html",
    col.names = c("Source type", "Color wheel", "Colorimeter", "Color wheel", "Colorimeter")
  ) %>%
  add_header_above(c(" " = 1, "Malawi" = 2, "Uganda" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

### Storage

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(storage)) %>%
  group_by(country, instrument, storage, test) %>%
  summarise(value = sum(!is.na(value))) %>%
  dplyr::filter(test == "TCR") %>%
  pivot_wider(
    values_from = value,
    names_from = instrument
  ) %>%
  ungroup %>%
  arrange(desc(`Color wheel`)) %>%
  pivot_wider(
    values_from = c(`Color wheel`, Colorimeter),
    names_from = country
  ) %>%
  select(
    storage, 
    ends_with("Malawi"),
    ends_with("Uganda")
  ) %>%
  kable(
    format = "html",
    col.names = c("Source type", "Color wheel", "Colorimeter", "Color wheel", "Colorimeter")
  ) %>%
  add_header_above(c(" " = 1, "Malawi" = 2, "Uganda" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(storage)) %>%
  group_by(country, storage, instrument, test) %>%
  dplyr::filter(sum(!is.na(value)) > 30) %>%
  ungroup %>%
  ggplot(
    aes(
      y = storage,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

### Water fetched by children

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(who_collected)) %>%
  group_by(country, instrument, who_collected, test) %>%
  summarise(value = sum(!is.na(value))) %>%
  dplyr::filter(test == "TCR") %>%
  pivot_wider(
    values_from = value,
    names_from = instrument
  ) %>%
  ungroup %>%
  arrange(desc(`Color wheel`)) %>%
  pivot_wider(
    values_from = c(`Color wheel`, Colorimeter),
    names_from = country
  ) %>%
  select(
    who_collected, 
    ends_with("Malawi"),
    ends_with("Uganda")
  ) %>%
  kable(
    format = "html",
    col.names = c("Source type", "Color wheel", "Colorimeter", "Color wheel", "Colorimeter")
  ) %>%
  add_header_above(c(" " = 1, "Malawi" = 2, "Uganda" = 2)) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

```{r}
test_long %>%
  dplyr::filter(!is.na(country), !is.na(who_collected)) %>%
  group_by(country, who_collected, instrument, test) %>%
  ungroup %>%
  ggplot(
    aes(
      y = who_collected,
      x = value,
      fill = country
    )
  ) +
  geom_boxplot(alpha = .5)  +
  theme +
  facet_grid(test ~ instrument, scales = "free") +
  scale_fill_viridis_d()
```

## Test wait time and chlorine residual

```{r}
hh %>%
  select(household_id, matches("(.)cr_c$"), matches("(.)cr_color$")) %>%
  pivot_longer(
    cols = -household_id,
    names_pattern = "(.*)(...)_(.*)",
    names_to = c("instrument", "test", ".value"),
    values_drop_na  = TRUE
  ) %>%
  group_by(instrument, test) %>%
  group_split %>%
  map(
    ~ lm(
      c ~ color,
      data = .x
    )
  ) %>%
  set_names(
    c(
      "Color wheel TCR", "Color wheel FCR",
      "Colorimeter TCR", "Colorimeter FCR"
    )
  ) %>%
  modelsummary(
    stars = TRUE,
    gof_omit = "IC|Log|RMSE|R2$"
  )
```

```{r}
hh %>%
  select(household_id, matches("(.)cr_c$"), matches("(.)cr_color$")) %>%
  pivot_longer(
    cols = -household_id,
    names_pattern = "(.*)(...)_(.*)",
    names_to = c("instrument", "test", ".value"),
    values_drop_na  = TRUE
  ) %>%
  dplyr::filter(!is.na(color)) %>%
  ggplot(
    aes(
      x = color,
      y = c
    )
  ) +
  geom_boxplot() +
  facet_grid(instrument ~ test, scales = "free_y")
```

```{r}
hh %>%
  select(household_id, matches("(.)cr_c$"), wp_turbidity) %>%
  pivot_longer(
    cols = -c(household_id, wp_turbidity),
    names_pattern = "(.*)(...)_c",
    names_to = c("instrument", "test"),
    values_drop_na  = TRUE
  ) %>%
  dplyr::filter(!is.na(wp_turbidity)) %>%
  ggplot(
    aes(
      y = wp_turbidity,
      x = value
    )
  ) +
  geom_boxplot() +
  xlim(0, 3) +
  facet_grid(instrument ~ test)
```

```{r}
hh %>%
  select(key, matches("(.)cr_c$"), wp_turbidity) %>%
  pivot_longer(
    cols = -c(key, wp_turbidity),
    names_pattern = "(.*)(...)_c",
    names_to = c("instrument", "test"),
    values_drop_na  = TRUE
  ) %>%
  dplyr::filter(!is.na(wp_turbidity)) %>%
  pivot_wider(
    id_cols = c(key, wp_turbidity, instrument),
    names_from = test,
    values_from = value
  ) %>%
  mutate(diff = tcr-fcr) %>%
  ggplot(
    aes(
      y = wp_turbidity,
      x = diff
    )
  ) +
  facet_wrap(~ instrument) +
  geom_boxplot()
```

## Enumerator fixed effects

> Enumerators typically use the same instrument (that is, the same colorimeter and the same color wheel), so we cannot separate clearly the effect of the enumerator and the instrument

```{r}
hh <-
  hh %>%
  group_by(village_id) %>%
  mutate(
    across(
      c(
        disctcr_c,
        discfcr_c, 
        meterfcr_c,
        metertcr_c
      ),
      ~ (. - mean(., na.rm = TRUE))
    )
  )
```

Unique values:

```{r}
hh %>%
  group_by(country) %>%
  summarise(
    across(
      c(enumerator_id, discid, meterid),
      ~ n_distinct(.)
    )
  ) %>%
  kable(
    format = "html"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

Number of disc readings per enumerator:

```{r}
hh %>%
  dplyr::filter(!is.na(disctcr)) %>%
  group_by(country, enumerator_id) %>%
  summarise(
    n = n()
  ) %>%
  group_by(country) %>%
  summarise(
    N = n(),
    mean = mean(n),
    sd = sd(n)
  ) %>%
  kable(
    format = "html"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

Number of colorimeter readings per enumerator:

```{r}
hh %>%
  dplyr::filter(!is.na(metertcr)) %>%
  group_by(country, enumerator_id) %>%
  summarise(
    n = n()
  ) %>%
  group_by(country) %>%
  summarise(
    N = n(),
    mean = mean(n),
    sd = sd(n)
  ) %>%
  kable(
    format = "html"
  ) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = TRUE,
    font_size = 14
  )
```

### Color wheel

#### Uganda

```{r}
hh %>% 
  dplyr::filter(country == "Uganda") %>%
  select(household_id, enumerator_id, disctcr_c, discfcr_c, village_id) %>%
  pivot_longer(
    cols = c(disctcr_c, discfcr_c),
    names_pattern = "disc(...)_c",
    names_to = "test"
  ) %>%
  group_by(test) %>%
  group_split %>%
  map(
    ~ feols(
        value ~ 0 + enumerator_id,
        data = .x
      ) %>%
      broom::tidy(
        conf.int = TRUE
      ) %>%
      mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper)
  ) %>%
  bind_rows %>%
  mutate(
    term = term %>% str_remove_all("enumerator_id")
  ) %>%
  ggplot(
    aes(
      y = term,
      x = estimate,
      xmin = conf.low,
      xmax = conf.high
    )
  ) +
  geom_errorbar() +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ test)
```

#### Malawi

```{r}
hh %>% 
  dplyr::filter(country == "Malawi") %>%
  select(household_id, enumerator_id, disctcr_c, discfcr_c) %>%
  pivot_longer(
    cols = c(disctcr_c, discfcr_c),
    names_pattern = "disc(...)_c",
    names_to = "test"
  ) %>%
  group_by(test) %>%
  group_split %>%
  map(
    ~ feols(
        value ~ 0 + enumerator_id,
        data = .x
      ) %>%
      broom::tidy(
        conf.int = TRUE
      ) %>%
      mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper)
  ) %>%
  bind_rows %>%
  mutate(
    term = term %>% str_remove_all("enumerator_id")
  ) %>%
  ggplot(
    aes(
      y = term,
      x = estimate,
      xmin = conf.low,
      xmax = conf.high
    )
  ) +
  geom_errorbar() +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ test)
```

### Colorimeter

#### Uganda

```{r}
hh %>% 
  dplyr::filter(country == "Uganda") %>%
  select(household_id, enumerator_id, metertcr_c, meterfcr_c) %>%
  pivot_longer(
    cols = c(metertcr_c, meterfcr_c),
    names_pattern = "meter(...)_c",
    names_to = "test"
  ) %>%
  group_by(test) %>%
  group_split %>%
  map(
    ~ feols(
        value ~ 0 + enumerator_id,
        data = .x
      ) %>%
      broom::tidy(
        conf.int = TRUE
      ) %>%
      mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper)
  ) %>%
  bind_rows %>%
  mutate(
    term = term %>% str_remove_all("enumerator_id")
  ) %>%
  ggplot(
    aes(
      y = term,
      x = estimate,
      xmin = conf.low,
      xmax = conf.high
    )
  ) +
  geom_errorbar() +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ test)
```

#### Malawi

```{r}
hh %>% 
  dplyr::filter(country == "Malawi") %>%
  select(household_id, enumerator_id, metertcr_c, meterfcr_c) %>%
  pivot_longer(
    cols = c(metertcr_c, meterfcr_c),
    names_pattern = "meter(...)_c",
    names_to = "test"
  ) %>%
  group_by(test) %>%
  group_split %>%
  map(
    ~ feols(
        value ~ 0 + enumerator_id,
        data = .x
      ) %>%
      broom::tidy(
        conf.int = TRUE
      ) %>%
      mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper)
  ) %>%
  bind_rows %>%
  mutate(
    term = term %>% str_remove_all("enumerator_id")
  ) %>%
  ggplot(
    aes(
      y = term,
      x = estimate,
      xmin = conf.low,
      xmax = conf.high
    )
  ) +
  geom_errorbar() +
  geom_point() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  facet_wrap(~ test)
```

<!-- ## Color wheel ID fixed effects -->

<!-- ### Uganda -->

<!-- ```{r} -->

<!-- hh %>%  -->

<!--   dplyr::filter(country == "Uganda") %>% -->

<!--   select(household_id, discid, disctcr_c, discfcr_c, village_id) %>% -->

<!--   mutate(discid = factor(discid)) %>% -->

<!--   pivot_longer( -->

<!--     cols = c(disctcr_c, discfcr_c), -->

<!--     names_pattern = "disc(...)_c", -->

<!--     names_to = "test" -->

<!--   ) %>% -->

<!--   group_by(test) %>% -->

<!--   group_split %>% -->

<!--   map( -->

<!--     ~ feols( -->

<!--         value ~ 0 + discid, -->

<!--         data = .x -->

<!--       ) %>% -->

<!--       broom::tidy( -->

<!--         conf.int = TRUE -->

<!--       ) %>% -->

<!--       mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper) -->

<!--   ) %>% -->

<!--   bind_rows %>% -->

<!--   mutate( -->

<!--     term = term %>% str_remove_all("discid") -->

<!--   ) %>% -->

<!--   ggplot( -->

<!--     aes( -->

<!--       y = term, -->

<!--       x = estimate, -->

<!--       xmin = conf.low, -->

<!--       xmax = conf.high -->

<!--     ) -->

<!--   ) + -->

<!--   geom_errorbar() + -->

<!--   geom_point() + -->

<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->

<!--   facet_wrap(~ test) -->

<!-- ``` -->

<!-- ### Malawi -->

<!-- ```{r} -->

<!-- hh %>%  -->

<!--   dplyr::filter(country == "Malawi") %>% -->

<!--   mutate(discid = factor(discid)) %>% -->

<!--   select(household_id, discid, disctcr_c, discfcr_c) %>% -->

<!--   pivot_longer( -->

<!--     cols = c(disctcr_c, discfcr_c), -->

<!--     names_pattern = "disc(...)_c", -->

<!--     names_to = "test" -->

<!--   ) %>% -->

<!--   group_by(test) %>% -->

<!--   group_split %>% -->

<!--   map( -->

<!--     ~ feols( -->

<!--         value ~ 0 + discid, -->

<!--         data = .x -->

<!--       ) %>% -->

<!--       broom::tidy( -->

<!--         conf.int = TRUE -->

<!--       ) %>% -->

<!--       mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper) -->

<!--   ) %>% -->

<!--   bind_rows %>% -->

<!--   mutate( -->

<!--     term = term %>% str_remove_all("enumerator_id") -->

<!--   ) %>% -->

<!--   ggplot( -->

<!--     aes( -->

<!--       y = term, -->

<!--       x = estimate, -->

<!--       xmin = conf.low, -->

<!--       xmax = conf.high -->

<!--     ) -->

<!--   ) + -->

<!--   geom_errorbar() + -->

<!--   geom_point() + -->

<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->

<!--   facet_wrap(~ test) -->

<!-- ``` -->

<!-- ## Colorimeter ID fixed effects -->

<!-- ### Uganda -->

<!-- ```{r} -->

<!-- hh %>%  -->

<!--   dplyr::filter(country == "Uganda") %>% -->

<!--   select(household_id, meterid, metertcr_c, meterfcr_c, village_id) %>% -->

<!--   mutate(meterid = factor(meterid)) %>% -->

<!--   pivot_longer( -->

<!--     cols = c(metertcr_c, meterfcr_c), -->

<!--     names_pattern = "disc(...)_c", -->

<!--     names_to = "test" -->

<!--   ) %>% -->

<!--   group_by(test) %>% -->

<!--   group_split %>% -->

<!--   map( -->

<!--     ~ feols( -->

<!--         value ~ 0 + meterid, -->

<!--         data = .x -->

<!--       ) %>% -->

<!--       broom::tidy( -->

<!--         conf.int = TRUE -->

<!--       ) %>% -->

<!--       mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper) -->

<!--   ) %>% -->

<!--   bind_rows %>% -->

<!--   mutate( -->

<!--     term = term %>% str_remove_all("meterid") -->

<!--   ) %>% -->

<!--   ggplot( -->

<!--     aes( -->

<!--       y = term, -->

<!--       x = estimate, -->

<!--       xmin = conf.low, -->

<!--       xmax = conf.high -->

<!--     ) -->

<!--   ) + -->

<!--   geom_errorbar() + -->

<!--   geom_point() + -->

<!--   geom_vline(xintercept = 0, linetype = "dashed") + -->

<!--   facet_wrap(~ test) -->

<!-- ``` -->

<!-- ### Malawi -->

<!-- ```{r} -->

<!-- hh %>%  -->

<!--   dplyr::filter(country == "Malawi") %>% -->

<!--   select(household_id, meterid, metertcr_c, meterfcr_c, village_id) %>% -->

<!--   mutate(meterid = factor(meterid)) %>% -->

<!--   pivot_longer( -->

<!--     cols = c(metertcr_c, meterfcr_c), -->

<!--     names_pattern = "disc(...)_c", -->

<!--     names_to = "test" -->

<!--   ) %>% -->

<!--   group_by(test) %>% -->

<!--   group_split %>% -->

<!--   map( -->

<!--     ~ feols( -->

<!--         value ~ 0 + meterid, -->

<!--         data = .x -->

<!--       ) %>% -->

<!--       broom::tidy( -->

<!--         conf.int = TRUE -->

<!--       ) %>% -->

<!--       mutate(test = .x %>% pull(test) %>% unique %>% str_to_upper) -->

<!--   ) %>% -->

<!--   bind_rows %>% -->

<!--   mutate( -->

<!--     term = term %>% str_remove_all("meterid") -->

<!--   ) %>% -->

<!--   ggplot( -->

<!--     aes( -->

<!--       y = term, -->

<!--       x = estimate, -->

<!--       xmin = conf.low, -->

<!--       xmax = conf.high -->

<!--     ) -->

<!--   ) + -->

<!--   geom_errorbar() + -->

<!--   geom_point() + -->

<!--   geom_vline(xintercept = 0.05, linetype = "dashed") + -->

<!--   facet_wrap(~ test) -->

<!-- ``` -->

## Spotchecks

```{r}
library(haven)

# 213 rows, hh_id is NA for 20
spotcheck_uganda <-
  read_dta(
    file.path(
      path_box,
      "Data - SHARED WITH IPA",
      "Uganda",
      "02_Baseline",
      "03_Data Cleaning",
      "2_raw_data",
      "6_Spot Check Survey",
      "2_dta",
      "Household Survey Spot Check.dta"
    )
  )

# 
spotcheck_malawi <-
  read_dta(
    file.path(
      path_box,
      "Data - SHARED WITH IPA",
      "Malawi",
      "02_Baseline",
      "02_Data Management",
      "4_data",
      "4_monitoring",
      "1_Spotchecks",
      "Household Survey Spot Check.dta"
    )
  )
```

**COMMENTS**

-   chlorine test steps followed in c90% of cases in Malawi, with higher scores for color disc
-   chlorine test steps followed in almost 100% of cases in Uganda, but much smaller sample
-   readings for colorwheel are similar (not statistically different); indeed, on average the main enumerator's reading is higher than the checker's (exception: TCR in Uganda)

### Chlorine test steps

#### Malawi

```{r}
spotcheck_vars <- c(
  "colordisc_rinse", "colordisc_fill", "colordisc_wip", "colordisc_dpd",
  "colordisc_sachet", "colordisc_swirl", "colordisc_wait",
  "colordisc_light", "colordisc_wash", "meter_rinse", "meter_fill",
  "meter_blank", "meter_wipe", "meter_dpd", "meter_vials",
  "meter_sachet", "meter_swirl", "meter_wait", "meter_wash"
)

spotcheck_malawi %>% 
  select(all_of(spotcheck_vars)) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  dplyr::filter(value %in% c(0, 1)) %>%
  # group_by(variable) %>%
  summarise(
    n_ones = sum(value == 1),
    n_zeros = sum(value == 0),
    total = n(),
    share_correct = mean(value == 1)
  )  %>%
  kable(format = "html")
```

#### Uganda

```{r}
spotcheck_uganda %>%  # Change this line
  select(all_of(spotcheck_vars)) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "value") %>%
  dplyr::filter(value %in% c(0, 1)) %>%
  # group_by(variable) %>%
  summarise(
    n_ones = sum(value == 1),
    n_zeros = sum(value == 0),
    total = n(),
    share_correct = mean(value == 1)
  )  %>%
  kable(format = "html")
```

### Chlorine residual readings

#### Malawi

```{r}
spotcheck_malawi_test <-
  spotcheck_malawi %>%
  mutate(
    across(
      c(fcr, tcr),
      ~ case_when(abs(.) < 100 ~ .)
    )
  ) %>%
  dplyr::filter(
    !is.na(fcr) | !is.na(tcr),
    !is.na(hh_id),
    !hh_id %in% c("", "None", "-999", "N/A")
  ) %>% 
  select(hh_id, tcr, fcr) %>%
  inner_join(
    hh_final %>%
      dplyr::filter(country == "Malawi"),
    by = c("hh_id" = "household_id"),
    relationship = "many-to-many"
  ) %>%
  mutate(
    diff_tcr = disctcr - tcr, # if >0, then higher reading by enumerator than checker
    diff_fcr = discfcr - fcr,
    disctcr02 = tcr >= .2,
    discfcr02 = fcr >= .2
  ) 
```

```{r}
tcr_count <- 
  spotcheck_malawi_test %>%
  dplyr::filter(!is.na(disctcr) & !is.na(tcr)) %>%
  nrow

fcr_count <- 
  spotcheck_malawi_test %>%
  dplyr::filter(!is.na(discfcr) & !is.na(fcr)) %>%
  nrow
```

<!-- There are `r spotcheck_malawi_test %>% pull(hh_id) %>% n_distinct` households matched between spot check and survey data sets. `r tcr_count` have TCR readings with color wheel, and `r fcr_count` have FCR readings. -->

```{r}
spotcheck_malawi_test %>%
  ggplot(
    aes(
      x = tcr,
      y = disctcr
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.1,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dotted"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(
    position = "jitter",
    alpha = .5
  ) +
  geom_vline(xintercept = 0.2, color = "red") +
  geom_hline(yintercept = 0.2, color = "red") +
  theme +
  labs(
    x = "Spot checker",
    y = "Enumerator",
    title = "TCR"
  ) 
```

```{r}
spotcheck_malawi_test %>%
  ggplot(
    aes(
      x = fcr,
      y = discfcr
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.1,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dotted"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(
    position = "jitter",
    alpha = .5
  ) +
  geom_vline(xintercept = 0.2, color = "red") +
  geom_hline(yintercept = 0.2, color = "red") +
  theme +
  labs(
    x = "Spot checker",
    y = "Enumerator",
    title = "FCR"
  ) 
```

```{r}
tcr_test_malawi <- t.test(spotcheck_malawi_test$disctcr, spotcheck_malawi_test$tcr, paired = TRUE)
fcr_test_malawi <- t.test(spotcheck_malawi_test$discfcr, spotcheck_malawi_test$fcr, paired = TRUE)
```

-   TCR difference test p-value: `r round(tcr_test_malawi$p.value, 4)`
-   FCR difference test p-value: `r round(fcr_test_malawi$p.value, 4)`

#### Uganda

```{r}
spotcheck_uganda_test <-
  spotcheck_uganda %>%
  mutate(
    across(
      c(fcr, tcr),
      ~ case_when(abs(.) < 100 ~ .)
    )
  ) %>%
  dplyr::filter(
    !is.na(fcr) | !is.na(tcr),
    !is.na(hh_id),
    !hh_id %in% c("", "None", "-999", "N/A")
  ) %>% 
  select(hh_id, tcr, fcr) %>%
  mutate(source = "Team lead") %>%
  inner_join(
    hh_final %>%
      dplyr::filter(country == "Uganda") %>%
      mutate(source = "Enumerator"),
    by = c("hh_id" = "household_id"),
    relationship = "many-to-many"
  ) %>%
  mutate(
    diff_tcr = disctcr - tcr, # if >0, then higher reading by enumerator than checker
    diff_fcr = discfcr - fcr,
    disctcr02 = tcr >= .2,
    discfcr02 = fcr >= .2
  ) 
```

```{r}
tcr_count <- 
  spotcheck_uganda_test %>%
  dplyr::filter(!is.na(disctcr) & !is.na(tcr)) %>%
  nrow

fcr_count <- 
  spotcheck_uganda_test %>%
  dplyr::filter(!is.na(discfcr) & !is.na(fcr)) %>%
  nrow
```

<!-- There are `r spotcheck_uganda_test %>% pull(hh_id) %>% n_distinct` households matched between spot check and survey data sets. `r tcr_count` have TCR readings with color wheel, and `r fcr_count` have FCR readings. -->

```{r}
spotcheck_uganda_test %>%
  ggplot(
    aes(
      x = tcr,
      y = disctcr
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.1,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dotted"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(
    position = "jitter",
    alpha = .5
  ) +
  geom_vline(xintercept = 0.2, color = "red") +
  geom_hline(yintercept = 0.2, color = "red") +
  theme +
  labs(
    x = "Spot checker",
    y = "Enumerator",
    title = "TCR"
  ) 
```

```{r}
spotcheck_uganda_test %>%
  ggplot(
    aes(
      x = fcr,
      y = discfcr
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.1,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dotted"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(
    position = "jitter",
    alpha = .5
  ) +
  geom_vline(xintercept = 0.2, color = "red") +
  geom_hline(yintercept = 0.2, color = "red") +
  theme +
  labs(
    x = "Spot checker",
    y = "Enumerator",
    title = "FCR"
  ) 
```

```{r}
spotcheck_uganda_test %>%
  summarize(
    N = n(),
    diff_tcr_mean = mean(diff_tcr, na.rm = TRUE),
    diff_fcr_mean = mean(diff_fcr, na.rm = TRUE)
  ) %>%
  kable(format = "html")
```

```{r}
tcr_test_uganda <- t.test(spotcheck_uganda_test$disctcr, spotcheck_uganda_test$tcr, paired = TRUE)
fcr_test_uganda <- t.test(spotcheck_uganda_test$discfcr, spotcheck_uganda_test$fcr, paired = TRUE)
```

-   TCR difference test p-value: `r round(tcr_test_uganda$p.value, 4)`
-   FCR difference test p-value: `r round(fcr_test_uganda$p.value, 4)`

### Chlorine detection rates

```{r}
mw_tcr <- 
  map(
  c("disctcr_02", "disctcr02"),
  ~ lm(
    paste(., "~ 1") %>% as.formula,
    data = spotcheck_malawi_test %>%
      dplyr::filter(!is.na(disctcr), !is.na(tcr))
  ) %>% tidy(conf.int = TRUE)
) %>% 
  bind_rows() %>%
  mutate(
    source = c("Enumerator", "Spot checker"),
    test = "TCR",
    country = "Malawi"
  )

mw_fcr <- 
  map(
  c("discfcr_02", "discfcr02"),
  ~ lm(
    paste(., "~ 1") %>% as.formula,
    data = spotcheck_malawi_test %>%
      dplyr::filter(!is.na(disctcr), !is.na(tcr))
  ) %>% tidy(conf.int = TRUE)
) %>% 
  bind_rows() %>%
  mutate(
    source = c("Enumerator", "Spot checker"),
    test = "FCR",
    country = "Malawi"
  )

ug_tcr <- 
  map(
  c("disctcr_02", "disctcr02"),
  ~ lm(
    paste(., "~ 1") %>% as.formula,
    data = spotcheck_uganda_test %>%
      dplyr::filter(!is.na(disctcr), !is.na(tcr))
  ) %>% tidy(conf.int = TRUE)
) %>% 
  bind_rows() %>%
  mutate(
    source = c("Enumerator", "Spot checker"),
    test = "TCR",
    country = "Uganda"
  )

ug_fcr <- 
  map(
  c("discfcr_02", "discfcr02"),
  ~ lm(
    paste(., "~ 1") %>% as.formula,
    data = spotcheck_uganda_test %>%
      dplyr::filter(!is.na(disctcr), !is.na(tcr))
  ) %>% tidy(conf.int = TRUE)
) %>% 
  bind_rows() %>%
  mutate(
    source = c("Enumerator", "Spot checker"),
    test = "FCR",
    country = "Uganda"
  )
```

```{r}
mw_tcr %>%
  bind_rows(mw_fcr) %>%
  bind_rows(ug_fcr) %>%
  bind_rows(ug_tcr) %>%
  ggplot(
    aes(
      x = estimate * 100,
      xmin = conf.low * 100,
      xmax = conf.high * 100,
      y = source,
      color = source
    )
  ) +
  geom_errorbar(width = .3) +
  geom_point(size = 2) +
  facet_grid(test ~ country) +
  theme +
  labs(
    y = NULL,
    x = "Percent of readings >= 0.2 ppm"
  )
```