# Water point census

```{r}
library(stringr)
library(sf)
library(tidyverse)
```

## Field observations

- In some villages, the promoters filled the dispenser after they saw the FOs inspecting it
- There is one DSW village that has an ILC device. The community guide reported that the ILC is operated by an organization called "Salvation"


```{r}
wp_census <-
  read_rds(
    file.path(
      path_box,
      "Data",
      "WaterPointCensus",
      "DataSets",
      "Final",
      "wp-census.rds"
    )
  ) %>%
  st_drop_geometry
```

## Number of water points found

```{r}
wp_census %>%
  select(wp_func, wp_dsw, wp_ilc_device, wp_ilc) %>%
  mutate(
    dsw_func = case_when(wp_dsw == 1 ~ wp_func),
    ilcwp_func = case_when(wp_ilc_device == 1 ~ wp_func),
    ilcwcp_func = case_when(wp_ilc == 1 ~ wp_func),
  ) %>%
  summarise(
    wp_n = n(),
    across(
      c(
        dsw_n = wp_dsw,
        ilcwp_n = wp_ilc_device,
        ilcwcp_n = wp_ilc
      ),
      ~ sum(., na.rm = TRUE)
    ),
    across(
      ends_with("func"),
      ~ (mean(., na.rm = TRUE) * 100) %>% round(1)
    )
  ) %>%
  pivot_longer(
    cols = everything(),
    names_pattern = "(.*)_(.*)",
    names_to = c("type", ".value")
  ) %>%
  set_names(c(" ", "N", "Percent functioning")) %>%
  mutate(
    ` ` = c("All water points", "DSW", "ILC water points", "ILC water collection points")
  )
```
## Type of water points

### All water points

```{r}
wp_census %>%
  group_by(sourcetype, wp_ilc_device, wp_dsw, wp_ilc) %>%
  summarise(
    n = n()
  ) %>%
  mutate(
    ea = case_when(
      wp_ilc_device ~ "ILC water point",
      wp_ilc ~ "ILC water collection point",
      wp_dsw ~ "DSW",
      TRUE ~ "Non-program"
    )
  ) %>%
  group_by(sourcetype) %>%
  mutate(
    total = sum(n),
    # sourcetype = reorder(sourcetype, total, order = TRUE)
  ) %>%
  ggplot(
    aes(
      y = sourcetype,
      x = n,
      fill = ea
    )
  ) +
  geom_col() +
  geom_text(
    aes(
      x = total,
      label = total
    ),
    size = 3,
    hjust = 1.2,
    color = "white"
  ) +
  theme +
  scale_fill_viridis_d() +
  labs(
    y = NULL,
    x = "Number of sources",
    fill = NULL
  )
```

### Program water points

```{r}
wp_census %>%
  mutate(
    ea = case_when(
      wp_ilc_device ~ "ILC",
      wp_ilc ~ "ILC water collection point",
      wp_dsw ~ "DSW"
    )
  ) %>%
  dplyr::filter(!is.na(ea)) %>%
  group_by(sourcetype, ea) %>%
  summarise(n = n()) %>%
  group_by(ea) %>%
  mutate(
    total = sum(n),
    pct = (n/total) * 100
  ) %>%
  ggplot(
    aes(
      y = sourcetype,
      x = pct,
      fill = ea,
      label = pct %>% round(1)
    )
  ) + 
  geom_col() +
  geom_text(
    aes(color = ea),
    size = 3,
    hjust = 1.2
  ) +
  facet_wrap(~ ea) +
  theme +
  scale_fill_viridis_d() +
  scale_color_viridis_d(direction = -1) +
  labs(
    y = NULL,
    x = "Percent of sources",
    fill = NULL
  )
```

## Number of water points per village

```{r}
wp_census %>%
  group_by(village_id) %>%
  summarise(
    `Water points` = n(),
    `DSW water points` = sum(wp_dsw, na.rm = TRUE) %>% na_if(0),
    `ILC water points` = sum(wp_ilc_device, na.rm = TRUE) %>% na_if(0),
    `ILC water collection points` = sum(wp_ilc, na.rm = TRUE) %>% na_if(0)
  ) %>%
  summarise(
    across(
      - village_id,
      ~ mean(., na.rm = TRUE),
      .names = "Average_{.col}"
    ),
    across(
      - village_id,
      ~ min(., na.rm = TRUE),
      .names = "Minimum_{.col}"
    ),
    across(
      - village_id,
      ~ max(., na.rm = TRUE),
      .names = "Maximum_{.col}"
    )
    ,
    across(
      - village_id,
      ~ sum(!is.na(.), na.rm = TRUE),
      .names = "N_{.col}"
    )
  ) %>%
  pivot_longer(
    cols = everything(),
    names_pattern = "(.*)_(.*)",
    names_to = c(".value", "Type")
  ) %>%
  select(
    Type, N, Average, Minimum, Maximum
  ) %>%
  rename(
    `Number of villages` = N
  )
```
## Water point functionality rate

- Overall: `r (wp_census %>% pull(wp_func) %>% mean* 100) %>% round(1)`%
- DSW: `r (wp_census %>% dplyr::filter(wp_dsw) %>% pull(wp_func) %>% mean* 100) %>% round(1)`%
- ILC water points: `r (wp_census %>% dplyr::filter(wp_ilc_device) %>% pull(wp_func) %>% mean* 100) %>% round(1)`%
- ILC water collection points: `r (wp_census %>% dplyr::filter(wp_ilc) %>% pull(wp_func) %>% mean * 100) %>% round(1)`%

## Share of paid water points

- Overall: `r (wp_census %>% pull(wp_pay) %>% mean* 100) %>% round(1)`%
- DSW: `r (wp_census %>% dplyr::filter(wp_dsw) %>% pull(wp_pay) %>% mean* 100) %>% round(1)`%
- ILC water points: `r (wp_census %>% dplyr::filter(wp_ilc_device) %>% pull(wp_pay) %>% mean* 100) %>% round(1)`%
- ILC water collection points: `r (wp_census %>% dplyr::filter(wp_ilc) %>% pull(wp_pay) %>% mean * 100) %>% round(1)`%

## DSW water points

```{r}
dsw <-
  wp_census %>%
  dplyr::filter(wp_dsw == 1)
```

### Functionality

```{r}
dsw %>%
  summarise(
    across(
      c(
        `Water point is functional` = wp_func,
        `Casing is present` = disp_casing_present,
        `PVC pole is present` = disp_pvc_pole_present,
        `Tank is present` = disp_tank_present,
        `Valve is working (conditional on tank being present)` = jc_valve,
        `Dispenser is not empty (conditional on valve working)` = jc_chlorine
      ),
      ~ (mean(., na.rm = TRUE) * 100) %>% round(1),
      .names = "{.col}_Percent"
    ),
    across(
      c(
        `Water point is functional` = wp_func,
        `Casing is present` = disp_casing_present,
        `PVC pole is present` = disp_pvc_pole_present,
        `Tank is present` = disp_tank_present,
        `Valve is working (conditional on tank being present)` = jc_valve,
        `Dispenser is not empty (conditional on valve working)` = jc_chlorine
      ),
      ~ sum(!is.na(.)),
      .names = "{.col}_N Obs"
    ),
    across(
      c(
        `Water point is functional` = wp_func,
        `Casing is present` = disp_casing_present,
        `PVC pole is present` = disp_pvc_pole_present,
        `Tank is present` = disp_tank_present,
        `Valve is working (conditional on tank being present)` = jc_valve,
        `Dispenser is not empty (conditional on valve working)` = jc_chlorine
      ),
      ~ sum(., na.rm = TRUE),
      .names = "{.col}_Count"
    )
  ) %>%
  pivot_longer(
    everything(),
    names_pattern = "(.*)_(.*)",
    names_to = c(" ", ".value")
  ) %>%
  select(" ", `N Obs`, Count, Percent)
```


### Chlorine dosage

```{r}
dsw %>%
  ggplot(
    aes(
      x = jc_mldispensed,
      fill = as.factor(jc_mllost)
    )
  ) +
  geom_vline(
    xintercept = 2.8,
    color = "gray",
    linetype = "dashed"
  ) +
  geom_vline(
    xintercept = 3.2,
    color = "gray",
    linetype = "dashed"
  ) +
  geom_histogram() +
  scale_fill_viridis_d() +
  theme +
  labs(
    y = "Number of dispensers",
    x = "Chlorine dose (mL)",
    fill = "Some chlorine leaked out of the calibrated cylinder"
  )
```

### Chlorine residual distribution

```{r}
dsw %>%
  select(
    `Color wheel_TCR` = disctcr_c, 
    `Color wheel_FCR` = discfcr_c, 
    Colorimeter_TCR = metertcr_c,
    Colorimeter_FCR = meterfcr_c
  ) %>%
  pivot_longer(
    cols = everything(),
    names_pattern = "(.*)_(.*)",
    names_to = c("instrument", "test")
  ) %>%
  ggplot(
    aes(
      x = value,
      fill = instrument
    )
  ) +
  scale_fill_viridis_d() + 
  geom_histogram() +
  facet_grid(test ~ instrument) +
  theme +
  labs(
    x = "Chlorine residual reading (mg/L)",
    y = "Number of tests"
  ) + 
  theme(legend.position = "none")
```
