# Water point chlorine residual tests

```{r}
library(stringr)
library(sf)
library(tidyverse)
library(modelsummary)
library(fixest)
```

<!-- ## Field observations -->

```{r}
wp_test <-
  read_rds(
    file.path(
      path_box,
      "Data",
      "WaterPointCensus",
      "DataSets",
      "Constructed",
      "wp-chlorine.rds"
    )
  ) %>%
  rename_with(
    ~ .x %>% 
      str_replace_all("meter", "meter_") %>% 
      str_replace_all("disc", "disc_") %>%
      str_replace_all("cr_c$", "cr")
  ) %>%
  dplyr::filter(!is.na(country), !is.na(disc_fcr))
```

## Color wheel and colorimeter readings

```{r}
wp_test %>%
  select(wp_id, matches("(.)cr$")) %>%
  pivot_longer(
    cols = -wp_id,
    names_pattern = "(.*)_(.*)",
    names_to = c(".value", "test")
  ) %>%
  mutate(
    test = str_to_upper(test)
  ) %>%
  ggplot(
    aes(
      x = meter,
      y = disc,
      color = test
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = 0.2,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(position = "jitter") +
  theme +
  facet_wrap(~ test) +
  labs(
    x = "Colorimeter reading (mg/L)",
    y = "Color wheel reading (mg/L)",
    color = NULL
  ) + 
  scale_color_viridis_d() 
```

## TCR and FCR readings

```{r}
wp_test %>%
  select(wp_id, matches("_(.)cr$")) %>%
  pivot_longer(
    cols = -wp_id,
    names_pattern = "(.*)_(.*)",
    names_to = c("test", ".value")
  ) %>%
  mutate(
    test = case_when(test == "meter" ~ "Colorimeter", TRUE ~ "Color wheel")
  ) %>%
  rename(
    TCR = tcr,
    FCR = fcr
  ) %>%
  ggplot(
    aes(
      x = FCR,
      y = TCR,
      color = test
    )
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.1,
    color = "gray80",
    linetype = "dashed"
  ) +
  geom_abline(
    slope = 1,
    intercept = -0.2,
    color = "gray80",
    linetype = "dotted"
  ) +
  geom_abline(
    slope = 1,
    color = "gray80"
  ) +
  geom_point(position = "jitter") +
  theme +
  facet_wrap(~ test) +
  scale_color_viridis_d() +
  theme(legend.position = "none")
```

## Dosage and chlorine residual

```{r}
map(
  c("disc_tcr", "disc_fcr", "meter_tcr", "meter_fcr"),
  ~ lm(
    paste(.x, " ~ jc_mldispensed + jc_mllost") %>% as.formula,
    data = wp_test
  )
) %>%
  set_names(
    c(
      "Color wheel TCR", "Color wheel FCR",
      "Colorimeter TCR", "Colorimeter FCR"
    )
  ) %>%
  modelsummary(
    stars = TRUE,
    gof_omit = "IC|Log|RMSE|R2$"
  )
```

## Wait time and chlorine residual

```{r}
map(
  c(
    "disc_tcr ~ disc_fcr_dur_wait", 
    "disc_fcr ~ disc_tcr_dur_wait", 
    "meter_tcr ~ meter_fcr_dur_wait", 
    "meter_fcr ~ meter_tcr_dur_wait"
  ),
  ~ lm(
    as.formula(.x),
    data = wp_test
  )
) %>%
  set_names(
    c(
      "Color wheel TCR", "Color wheel FCR",
      "Colorimeter TCR", "Colorimeter FCR"
    )
  ) %>%
  modelsummary(
    stars = TRUE,
    gof_omit = "IC|Log|RMSE|R2$"
  )
```

## Reported color and chlorine residual

```{r}
map(
  c(
    "disc_tcr ~ disc_fcr_color", 
    "disc_fcr ~ disc_tcr_color", 
    "meter_tcr ~ meter_fcr_color", 
    "meter_fcr ~ meter_tcr_color"
  ),
  ~ lm(
    as.formula(.x),
    data = wp_test
  )
) %>%
  set_names(
    c(
      "Color wheel TCR", "Color wheel FCR",
      "Colorimeter TCR", "Colorimeter FCR"
    )
  ) %>%
  modelsummary(
    stars = TRUE,
    gof_omit = "IC|Log|RMSE|R2$"
  )
```

## Water source type and chlorine residual

```{r}
map(
  c(
    "disc_tcr ~ disc_fcr_color", 
    "disc_fcr ~ disc_tcr_color", 
    "meter_tcr ~ meter_fcr_color", 
    "meter_fcr ~ meter_tcr_color"
  ),
  ~ lm(
    as.formula(.x),
    data = wp_test
  )
) %>%
  set_names(
    c(
      "Color wheel TCR", "Color wheel FCR",
      "Colorimeter TCR", "Colorimeter FCR"
    )
  ) %>%
  modelsummary(
    stars = TRUE,
    gof_omit = "IC|Log|RMSE|R2$"
  )
```

## Turbidity and chlorine residual

```{r}
wp_test %>%
  ggplot(
    aes(
      x = wp_turbidity,
      fill = wp_turbidity
    )
  ) +
  geom_bar() +
  scale_fill_viridis_d() +
  theme +
  labs(
    y = "Number of water points",
    x = "Turbidity (1 = Clear, 5 = Very turbid)"
  ) +
  theme(
    legend.position = "none"
  )
```


```{r}
map(
  c(
    "disc_diff_c ~ wp_turbidity", 
    "meter_diff_c ~ wp_turbidity"
  ),
  ~ lm(
    as.formula(.x),
    data = wp_test
  )
) %>%
  set_names(
    c(
      "Color wheel difference",
      "Colorimeter difference"
    )
  ) %>%
  modelsummary(
    stars = TRUE,
    gof_omit = "IC|Log|RMSE|R2$"
  )
```


## Colorimeter IDs and chlorine residual

```{r}
wp_test %>% 
  dplyr::filter(!is.na(meter_id)) %>%
  group_by(meter_id) %>%
  mutate(meter_id = paste0(meter_id, " (N =", n(), ")")) %>%
  ggplot(
    aes(
      y = meter_id,
      x = meter_fcr
    )
  ) +
  geom_boxplot() +
  facet_grid(rows = vars(country), scales = "free") +
  theme +
  labs(
    y = NULL,
    x = "Free chlorine residual (mg/L)"
  )
```

```{r}
wp_test %>%
  dplyr::filter(!is.na(meter_id)) %>%
  group_by(meter_id) %>%
  mutate(meter_id = paste0(meter_id, " (N =", n(), ")")) %>%
  ggplot(
    aes(
      y = meter_id,
      x = meter_tcr
    )
  ) +
  geom_boxplot() +
  facet_grid(rows = vars(country), scales = "free") +
  theme +
  labs(
    y = NULL,
    x = "Total chlorine residual (mg/L)"
  )
```

## Color disc IDs and chlorine residual

```{r}
wp_test %>%
  dplyr::filter(!is.na(meter_id)) %>%
  group_by(disc_id) %>%
  mutate(disc_id = paste0(meter_id, " (N =", n(), ")")) %>%
  ggplot(
    aes(
      y = disc_id,
      x = disc_fcr
    )
  ) +
  geom_boxplot() +
  facet_grid(rows = vars(country), scales = "free") +
  theme +
  labs(
    y = NULL,
    x = "Free chlorine residual (mg/L)"
  )
```

```{r}
wp_test %>%
  dplyr::filter(!is.na(meter_id)) %>%
  group_by(disc_id) %>%
  mutate(disc_id = paste0(meter_id, " (N =", n(), ")")) %>%
  ggplot(
    aes(
      y = disc_id,
      x = disc_tcr
    )
  ) +
  geom_boxplot() +
  facet_grid(rows = vars(country), scales = "free") +
  theme +
  labs(
    y = NULL,
    x = "Total chlorine residual (mg/L)"
  )
```

## Enumerator IDs and chlorine residual

